---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE, 
  fig.width = 10, 
  fig.height = 4
)
```
# pwdthemes

<!-- badges: start -->
<!-- badges: end -->

The goal of `pwdthemes` is to provide easy to use theme options for employees of the Philadelphia Water Department within R and Rmarkdown. This package provides color and fill options for `ggplot2` figures. It also provides rmarkdown templates that will allow people to easy produce Rmarkdown reports with PWD branding on them. 

## Installation

If you are within the PWD network, you can install the released version of pwdthemes from [PWD's Internal Package Directory](http://pwdrstudio/bls-cran/) with:

``` r
install.packages("pwdthemes", repos = "http://pwdrstudio/bls-cran/")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tbradley1013/pwdthemes")
```
**NOTE: you will have to have [RTools](https://cran.r-project.org/bin/windows/Rtools/) installed in order to install this package using either `install.packages` or `install_github` methods**

## `ggplot2` scales

This package provides functions that allow you to easily add PWD colors to `ggplot2` figures. These can be added using the `scale_color_pwd` and `scale_fill_pwd` functions depending on whether you are using the color or fill aesthetic. There are several different color options that are detailed in the help page, see `?pwd_pals`. These palettes are based on the [PWD Styleguide](http://waternet/news/The_New_Philadelphia_Water_Brand/PWD_StyleGuidelines.pdf), A few of them will be demonstrated here:

```{r}
library(pwdthemes)
library(ggplot2)
library(dplyr)
library(ggridges)
library(patchwork)
```

```{r}
large_diamonds <- diamonds %>% 
  filter(carat > 2)

pc <- ggplot(large_diamonds, aes(price, carat, color = cut)) + 
  geom_point() + 
  theme_bw()

pf <- ggplot(large_diamonds, aes(price, cut, fill = cut)) + 
  geom_density_ridges() + 
  theme_bw()
```

### Main

```{r, fig.width = 10, fig.height = 4}
pc_main <- pc + scale_color_pwd("main")
pf_main <- pf + scale_fill_pwd("main")

pc_main + pf_main
```


### Main Dark

```{r, fig.width = 10, fig.height = 4}
pc_main_d <- pc + scale_color_pwd("main_dark")
pf_main_d <- pf + scale_fill_pwd("main_dark")

pc_main_d + pf_main_d

```


### Dark

```{r, fig.width = 10, fig.height = 4}
pc_dark <- pc + scale_color_pwd("dark")
pf_dark <- pf + scale_fill_pwd("dark")

pc_dark + pf_dark

```


### View PWD Palettes
