---
title: "PWD Color Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PWD Color Palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8, 
  fig.height = 4,
  warning = FALSE,
  message = FALSE
)
```

# Introduction

The `pwdthemes` R package includes several color palettes that are based on the style guide provided by the Public Affairs division of the Philadelphia Water Department (PWD). These palettes can be accessed using the `pwd_pals()` functional or more easily through the `scale_color_pwd` and `scale_fill_pwd` ggplot2 scale functions. This guide displays what the full palettes look like. 

```{r setup}
library(ggplot2)
library(patchwork)
library(ggridges)
library(pwdthemes)
```

First, I will create the base figures and define a helper function to render the different figures with each palette
```{r define-funs}
large_diamonds <- diamonds[diamonds$carat > 2.2, ]

pc <- ggplot(large_diamonds, aes(price, carat, color = cut)) + 
  geom_point() + 
  theme_pwd()

pf <- ggplot(large_diamonds, aes(price, cut, fill = cut)) + 
  geom_density_ridges() + 
  theme_pwd()

display_pals <- function(p1 = pc, p2 = pf, pal){
  p1_out <- p1 + scale_color_pwd(pal)
  p2_out <- p2 + scale_fill_pwd(pal)
  
  out <- p1_out + p2_out
  
  return(out)
}

```



# Main 

```{r main}
pc_main <- pc + scale_color_pwd("main")
pf_main <- pf + scale_fill_pwd("main")

pc_main + pf_main

view_pwd_palette("main")
```


# Main Dark

```{r main-dark}
pc_main_dark <- pc + scale_color_pwd("main_dark")
pf_main_dark <- pf + scale_fill_pwd("main_dark")

pc_main_dark + pf_main_dark

view_pwd_palette("main_dark")
```


# Main Light

```{r main-light}
pc_main_light <- pc + scale_color_pwd("main_light")
pf_main_light <- pf + scale_fill_pwd("main_light")

pc_main_light + pf_main_light

view_pwd_palette("main_light")
```


# Highlights 

```{r highlights}
pc_hl <- pc + scale_color_pwd("highlights")
pf_hl <- pf + scale_fill_pwd("highlights")

pc_hl + pf_hl

view_pwd_palette("highlights")
```


# Highlights Dark

```{r highlights-dark}
pc_hl_dark <- pc + scale_color_pwd("highlights_dark")
pf_hl_dark <- pf + scale_fill_pwd("highlights_dark")

pc_hl_dark + pf_hl_dark

view_pwd_palette("highlights_dark")
```


# Highlights Light

```{r highlights-light}
pc_hl_light <- pc + scale_color_pwd("highlights_light")
pf_hl_light <- pf + scale_fill_pwd("highlights_light")

pc_hl_light + pf_hl_light

view_pwd_palette("highlights_light")
```


# Map 

```{r map}
pc_map <- pc + scale_color_pwd("map")
pf_map <- pf + scale_fill_pwd("map")

pc_map + pf_map

view_pwd_palette("map")
```


# Map Dark

```{r map-dark}
pc_map_dark <- pc + scale_color_pwd("map_dark")
pf_map_dark <- pf + scale_fill_pwd("map_dark")

pc_map_dark + pf_map_dark

view_pwd_palette("map_dark")
```


# Map Light 

```{r map-light}
pc_map_light <- pc + scale_color_pwd("map_light")
pf_map_light <- pf + scale_fill_pwd("map_light")

pc_map_light + pf_map_light

view_pwd_palette("map_light")
```


# Dark

```{r dark}
pc_dark <- pc + scale_color_pwd("dark")
pf_dark <- pf + scale_fill_pwd("dark")

pc_dark + pf_dark

view_pwd_palette("dark")
```


# Light

```{r light}
pc_light <- pc + scale_color_pwd("light")
pf_light <- pf + scale_fill_pwd("light")

pc_light + pf_light

view_pwd_palette("light")
```


# Full

```{r full}
pc_full <- pc + scale_color_pwd("full")
pf_full <- pf + scale_fill_pwd("full")

pc_full + pf_full

view_pwd_palette("full")
```
